\textbf{ZKLoRA: Efficient Zero-Knowledge Proofs for LoRA Verification}

### 2025-01-17 paper/main.tex
rough draft first figure

>>>>

\begin{figure}[ht]
\centering
\begin{tikzpicture}[
    font=\small,
    >=latex,
    thick,
    node distance=1.6cm,
    stepbox/.style={
      draw,
      rounded corners,
      minimum width=6.2cm,
      minimum height=2.4cm,
      align=center,
      fill=gray!10,
      font=\bfseries
    },
    subblock/.style={
      draw,
      rounded corners,
      align=center,
      minimum width=1.6cm,
      minimum height=0.8cm,
      fill=gray!20,
      font=\scriptsize
    },
    arrow/.style={->, thick},
]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Step 1 BOX (Multi-Party Inference)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\node[stepbox,
      label={[above=2pt]:{\footnotesize \textbf{Step 1: Multi-Party Inference}}}] (step1) 
{\vspace{4pt}};  % minimal text inside, slight vertical spacing

% Inside Step 1: Two sub-blocks horizontally
\node[subblock,
      label={[font=\scriptsize]above:{Base Model User}},
      anchor=center, 
      xshift=-1.6cm,
      yshift=-0.4cm] 
(bmuser) at (step1.center)
{};

\node[subblock,
      label={[font=\scriptsize]above:{LoRA Contributor}},
      anchor=center, 
      xshift=+1.6cm,
      yshift=-0.4cm] 
(lorablk) at (step1.center)
{};

% Two separate arrows: "Base Acts" & "LoRA Acts"
\draw[arrow] 
  ([yshift=-0.05cm]bmuser.east) 
    to[bend left=20] 
  node[midway, above, yshift=-0.1cm, font=\scriptsize]{Base Acts}
  ([yshift=-0.05cm]lorablk.west);

\draw[arrow] 
  ([yshift=-0.25cm]lorablk.west) 
    to[bend right=20] 
  node[midway, below, yshift=+0.1cm, font=\scriptsize]{LoRA Acts}
  ([yshift=-0.25cm]bmuser.east);

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Step 2 BOX (Proof Generation), below step1
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\node[stepbox, fill=orange!15, 
      label={[above=2pt]:{\footnotesize \textbf{Step 2: Proof Generation}}}, 
      below=of step1] (step2)
{\footnotesize LoRA Contributor \\
Builds Zero-Knowledge Proofs};

% Arrow from step1 -> step2 with text "LoRA input/output acts"
\draw[arrow] (step1.south) -- node[left, xshift=-0.1cm, font=\scriptsize]{LoRA input/output acts} (step2.north);

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Step 3 BOX (Verification), below step2
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\node[stepbox, fill=blue!10, 
      label={[above=2pt]:{\footnotesize \textbf{Step 3: Verification}}}, 
      below=of step2] (step3)
{\footnotesize Base Model User \\
Verifies each proof};

% Arrow from step2 -> step3
\draw[arrow] (step2.south) -- node[left, font=\scriptsize]{\textit{proof files}} (step3.north);

\end{tikzpicture}
\caption{\textbf{Three-Step ZKLoRA Process (Vertical).}
\textbf{(1)} Base Model User and LoRA Contributor exchange ``Base Acts'' and ``LoRA Acts'' in a full multi-party inference. 
\textbf{(2)} The LoRA Contributor generates cryptographic proofs for correctness. 
\textbf{(3)} The Base Model User verifies these proofs, ensuring correct LoRA alignment without revealing private adapter weights.}
\label{fig:zklora_3steps}
\end{figure}
